The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-31 paper.tex
update

In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\

@@

where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light, $m_{\text{e}}$ electron mass,\
$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum,\
$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic enough to\
produce scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
We set $\gamma_{\text{max}}$ to be $10^{6}$, corresponding to the cutoff CRe energy $0.5$ GeV.

To  we integrate the incident photon energy from\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
$\epsilon_{\text{max}}=13.59$ eV (starlight).

The gamma-ray emissivity\
is computed for each computational volume element in our simulations\
using the Klein–Nishina IC cross-section \citep{Jones1968} based\
on the simulated CR number density and the ISRF model given by \citet{Porter2017}.

@@

>>>>

In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution with a spectral index 2 and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\

@@

where $\sigma_{T}$ is the Thomson cross section, $c$ speed of light, $m_{\text{e}}$ electron mass,\
$n(\epsilon)$ the photon number density of ISRF per energy, $\gamma$ the Lorentz factor of CRe,\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of CRe power-law spectrum,\
$\gamma_{\text{min}}(\epsilon)$ is the minimum required Lorentz factor of CRe such that CRe is energetic sufficient for\
producing scattered photon at the energy $\epsilon_{1}$ from an incident photon energy $\epsilon$.\
$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum, i.e. $\gamma_{\text{max}}=10^{6}$.

Since the ISRF is dominated by the cosmic microwave background (CMB)\
at high latitudes and optical starlight at low latitudes,\

we integrate the incident photon energy from\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (CMB radiation) to\
$\epsilon_{\text{max}}=13.59$ eV (starlight).

The gamma-ray emissivity\
is computed for each computational cell in our simulations\
using the Klein–Nishina IC cross-section \citep{Jones1968} based\
on the simulated CR number density and the ISRF model given by \citet{Porter2017}.

@@

\begin{equation}
I = \frac{1}{\epsilon_{1}}\int \frac{dE}{dtd\epsilon_{1}dV} dl,
\end{equation}
